Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-27 submission/Sze_Obesity_PeerJ_2016.Rmd
edit Figure 5 legend

>>>>

**Figure 5: Overall Accuracy of Each Study to Predict Non-Obese and Obese Individuals based on that Study's Classification Variables** Overall there is no significant difference between the studes in mean accuracy.  Additionally, the accuracy for each study group to predict Non-Obese and Obese individuals was relatively low.
